Boson-Sampling with Single Photons: A Roadmap to Post-Classical Computation

### 2016-09-29 paper.tex
added appendix and fixed it up - corrections to do

%
% Acknowledgments
%

\begin{acknowledgments}
\end{acknowledgments}

\appendix

\section{Numerically modelling the effects of signal-to-noise ratios}

\section{Details of scattershot boson-sampling analysis}

>>>>

\begin{acknowledgments}
\end{acknowledgments}
\appendix

\section{Numerically modelling the effects of signal-to-noise ratios} \label{app:A}

Here we provide more details on the reasonable range of the signal-to-noise ratio (SNR) of boson-sampling output data. More specifically, we use a Bayesian approach \cite{bib:90} to validate ideal boson-sampling (\mbox{$SNR\to\infty$}) against hypothetical mixed sampling (SNR equals some finite value). For the sake of simplicity, the hypothetical sampling is mixing between ideal boson-sampling and thermal state sampling \cite{bib:91}. As shown in Fig.~\ref{fig:SNR}, given \mbox{$n = 5$} and \mbox{$m = 10$}, only if \mbox{$SNR > 1.8$}, the Bayesian analysis can reach a relatively high success rate. Accordingly, we suppose \mbox{$SNR = 2$} as a minimum requirement in the App.~\ref{app:B}.

\begin{figure*}[!htb]
\includegraphics[width=1.6\columnwidth]{SNR}
\caption{Bayesian approach to validate ideal boson-sampling (\mbox{$SNR\to\infty$}) against hypothetical mixed sampling (SNR equals some finite value). Here we set \mbox{$n=5$}, \mbox{$m=10$}. In all plots, blue shaded regions correspond to one standard deviations of the boson-sampling validation, obtained by averaging over a numerical simulation with 1,000 Haar-uniform unitary matrices. (a) \mbox{$SNR = 1.0$}, success rate: \mbox{$(0 \pm 0)\% $}; (b) \mbox{$SNR = 1.2$}, success rate: \mbox{$(3 \pm 17)\% $}; (c) \mbox{$SNR = 1.4$}, success rate: \mbox{$(57 \pm 49)\% $}; (d) \mbox{$SNR = 1.6$}, success rate: \mbox{$(96 \pm 19)\% $}; (e) \mbox{$SNR = 1.8$}, success rate: \mbox{$(100 \pm 0)\%$}; (f) \mbox{$SNR = 2.0$}, success rate: \mbox{$(100 \pm 0)\% $}.} \label{fig:SNR}
\end{figure*}

\section{Details of scattershot boson-sampling analysis} \label{app:B}

\subsection{Case 1}

First, let us start from the case without shutters or resolving single photon detectors.

Suppose among $m$ SPDC sources, the number of sources generating single-photon is $s$ and generating twin-photon is $t$. For inefficient and non-resolving detectors, the probability of such event is,
\begin{align} \label{eq:1}
{P_\mathrm{gen}}(s,t) = {p^s}{p^{2t}}{(1 - p - {p^2})^{m - s - t}}\binom{m}{s,t},
\end{align}
where $p$ is the single-photon generating efficiency of each SPDC source.

Given $s$ single-photons, the probability of coupling successfully $z$ single-photons to the circuit is,
\begin{align} \label{eq:2}
{P_\mathrm{1in}}(s,z) = p_\mathrm{in}^{z}{(1 - {p_\mathrm{in}})^{s - z}} \binom{s}{z},
\end{align}
where ${p_\mathrm{in}}$ is the single-photon coupling efficiency.

Given $s$ single-photons, the probability of detecting ${n_1}$ single-photons is,
\begin{align} \label{eq:3}
{P_\mathrm{1d}}(s,{n_1}) = {\eta ^{{n_1}}}{(1 - \eta )^{s - {n_1}}}\binom{s}{n_1},
\end{align}
where $\eta$ is the single-photon detecting efficiency.

Given $t$ twin-photons, the probability of coupling successfully $x$ twin-photons and $y$ single-photons to the circuit is,
\begin{align} \label{eq:4}
{P_\mathrm{2in}}(t,x,y) = p_\mathrm{in}^{2x}{[2{p_\mathrm{in}}(1 - {p_\mathrm{in}})]^y} {(1 - {p_\mathrm{in}})^{2(t - x - y)}} \binom{t}{x,y}.
\end{align}

Given $t$ twin-photons, the probability that ${n_2}$ detectors will click is,
\begin{align} \label{eq:5}
{P_\mathrm{2d}} = {P_\mathrm{1d}}(\eta \to {\eta _2}),
\end{align}
where \mbox{${\eta _2} = \eta (2 - \eta )$} is the probability that a detector will click if a twin-photon is injected.

Satisfying the coincidence condition of $n$ triggering and $n$ counting after the circuit, the probability of getting a sample is of the form,
\begin{align} \label{eq:6}
&{P_{t(0,0)}} = \sum_{q = n}^m {\sum\limits_{t = 0}^q {{P_\mathrm{gen}}(q - t,t) }} \nonumber \\
&\cdot \sum_{n_1 = \max [n - t,0]}^{\min [q - t,n]} {{P_\mathrm{1d}}(q - t,{n_1})}{P_\mathrm{2d}}(t,n - {n_1}) \nonumber \\
&\cdot \sum_{2x + y + z \ge n} {{P_\mathrm{1in}}(q - t,z){P_\mathrm{2in}}(t,x,y)}{P_\mathrm{1d}}(2x + y + z,n),
\end{align}
where the subscript $t$ indicates the word ``total-probability'', and $(0,0)$ indicates the case without shutters or photon-number-resolving detectors.

However, the correct boson-sampling should be on condition that exactly $n$ heralded single photons are coupling to the circuit. Specifically, in the $s$ single-photon sources, the probability of triggering and coupling successfully ${n_1}$ single-photons to the circuit is,
\begin{align} \label{eq:7}
{P_\mathrm{1in1}}(s,{n_1}) = {({p_\mathrm{in}}\eta )^{{n_1}}} {[(1 - {p_\mathrm{in}})(1 - \eta )]^{s - {n_1}}} \binom{s}{n_1}.
\end{align}

In the $t$ twin-photon sources, the probability of triggering and coupling successfully ${n_2}$ single-photons to the circuit is,
\begin{align} \label{eq:8}
{P_\mathrm{2in1}}(t,{n_2}) &= {[2{p_\mathrm{in}}(1 - {p_{in}}){\eta_2}]^{{n_2}}} \nonumber \\
&\cdot {[{(1 - {p_\mathrm{in}})^2}(1 - {\eta _2})]^{t - {n_2}}}\binom{t}{n_2}.
\end{align}

Therefore, when $n$ coincidence counting are both recorded at heralding and at the output, the probability that it is a correct boson-sampling signal is given by,
\begin{align} \label{eq:9}
{P_{c(0,0)}} &= \sum_{q = n}^m {\sum_{t = 0}^q {{P_\mathrm{gen}}} } (q - t,t) \nonumber \\
&\cdot\sum_{{n_1} = \max [n - t,0]}^{\min [q - t,n]} {{P_\mathrm{1in1}}(q - t,{n_1})} {P_\mathrm{2in1}}(t,n - {n_1}){\eta ^n},
\end{align}
where the subscript $c$ indicates the word `correct'.

To ensure $SNR$ larger than two, which is quite a low requirement for correct sampling, we plot the requirement for coupling and detection efficiency when increasing $n$. As shown in Fig. 11(a), the requirements for detectors and coupling are rather high if without shutter or photon-number-resolving detectors. When the coupling efficiency is 0.9 and the detection efficiency is 0.95, we can only scale boson-sampling experiments to 4 photons.

\subsection{Case 2}

If employing shutters, but without photon-number-resolving detectors, we can apply some small modifications to the Eqs.~\ref{whichOne} \& \ref{whichOne} to obtain,
\begin{align} \label{eq:1011}
{P_{t(0,1)}} &= \sum_{q = n}^m {\sum_{t = 0}^q {{P_\mathrm{gen}}(q - t,t)\sum_{{n_1} = \max [n - t,0]}^{\min [q - t,n]} } } \nonumber \\
& {{P_\mathrm{1d}}(q - t,{n_1})}{P_\mathrm{2d}}(t,n - {n_1})\sum_{2x + y + z \ge n}  \nonumber \\
& {{P_\mathrm{1in}}({n_1},z){P_\mathrm{2in}}(n-{n_1},x,y)}{P_\mathrm{1d}}(2x + y + z,n), \nonumber \\
{P_{c(0,1)}} &= \sum_{q = n}^m {\sum_{t = 0}^q {{P_\mathrm{gen}}} } (q - t,t)\sum_{{n_1} = \max [n - t,0]}^{\min [q - t,n]} \nonumber \\
&{P_\mathrm{1in1}^\mathrm{shutter}(q - t,{n_1})} P_\mathrm{2in1}^\mathrm{shutter}(t,n - {n_1}){\eta^n},
\end{align}
where,
\begin{align} \label{eq:1213}
P_\mathrm{1in1}^\mathrm{shutter}(s,{n_1}) &= {({p_\mathrm{in}}\eta )^{{n_1}}}{(1 - \eta )^{s - {n_1}}}\binom{s}{n_1}, \nonumber \\
P_\mathrm{2in1}^\mathrm{shutter}(t,{n_2}) &= {[2{p_\mathrm{in}}(1 - {p_\mathrm{in}}){\eta_2}]^{{n_2}}} {(1 - {\eta _2})^{t - {n_2}}} \binom{t}{{n_2}}.
\end{align}

To satisfy \mbox{$SNR>2$}, we plot the requirements to achieve quantum supremacy with increasing photon number in Fig. 11(b). From the figure, we can see that when the size of a boson-sampler is relatively small, i.e. \mbox{$n = 3 \sim 4$}, the requirement for coupling efficiency is relaxed a little by employing the shutter. We can implement 4 photon SBS with 0.8 coupling efficiency and 0.95 detection efficiency without photon-number-resolving detectors.

\subsection{Case 3}

When coming to the case with photon-number-resolving detectors but without shutters, using \mbox{${\eta '_2}  = 2\eta (1 - \eta )$} to subsititude ${\eta _2}$ in Eqs.~\ref{eq:6} \& \ref{eq:9}, we have
\begin{align} \label{eq:1415}
{P_{t(1,0)}} = {P_{t(0,0)}}({\eta _2} \to {\eta '_2} ), \nonumber \\
{P_{c(1,0)}} = {P_{c(0,0)}}({\eta _2} \to {\eta '_2} ).
\end{align}

In the same way, to guarantee \mbox{$SNR > 2$}, we determine the lower bound for coupling efficiency and detection efficiency against the scaling of the SBS device. Comparing Figs.~\ref{fig:SNR}(a,c), if photon-number-resolving detectors of 0.95 detection efficiency were utilised, the quantum system could perform almost as well as a quantum system with perfect photodetectors that were non-photon-number-resolving.

\subsection{Case 4}

Finally, both shutters and photon-number-resolving detectors are available. Just employing Eq.~\ref{eq:1011}, and changing ${\eta _2}$ to ${\eta '_2} $ as we have done before, we obtain
\begin{align} \label{eq:1617}
{P_{t(1,1)}} &= {P_{t(0,1)}}({\eta _2} \to {\eta '_2} ), \nonumber \\
{P_{c(1,1)}} &= {P_{c(0,1)}}({\eta _2} \to {\eta '_2} ).
\end{align}

We are glad to see that, as shown in Fig.~\ref{fig:SNR}(d), the rigorous requirements in detection efficiency and coupling efficiency of the quantum system can be substantially loosened. And a SBS of 20 photons seems appears viable if the detection and coupling efficiency of the device can reach 0.95 and 0.8, respectively.
